%% SCPMA submission: HXMT/HE 1B saturation recovery
%%
%% TEMPLATE STATUS (T2): currently using stock article class as placeholder.
%% SCPMA template (scpma.cls or equivalent) deferred — official site cert
%% expired and Springer mirror returns 303 as of 2026-05-06. To swap:
%%   (1) obtain scpma.cls + matching .bst from co-author at IHEP, OR
%%   (2) email scpma@scichina.org requesting current author template, OR
%%   (3) initial submission can use this article-class PDF; SCPMA usually
%%       requests template-formatted re-submission only at acceptance.
%% When swapping: replace the documentclass line, migrate \author/\title
%% macros to template-specific \Author/\Title/\Address/\Email forms, and
%% verify Tasks 6-15 sectioning still resolves cleanly.
\documentclass[twocolumn]{article}

\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{xcolor}
\usepackage[a4paper,margin=2cm]{geometry}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue]{hyperref}

\graphicspath{{figures/}}

\title{Saturation Recovery for Insight-HXMT/HE\\Bright Burst Observations from Level-1B Raw Data}

\author{Hao-Xuan Guo\thanks{kuohaoxuanus@outlook.com} \and HXMT Collaboration (TBD)}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
TBD --- to be drafted in Task 16 after Phase E numbers are frozen.
The abstract will follow the structure in
\texttt{docs/superpowers/specs/2026-05-06-scpma-submission-design.md} \S2.2.
\end{abstract}

%% ===================================================================
\section{Introduction}\label{sec:intro}
%% Task 6
TBD --- ~1.5 pages. Hook + 1.1 HE in bright sources / 1.2 FIFO saturation
\& 1K limits / 1.3 1B opportunity \& challenges / 1.4 four contributions.

%% ===================================================================
\section{HE Data System and Saturation Mechanisms}\label{sec:instrument}
%% Task 7
TBD --- ~1.5 pages. Subsections 2.1 hardware path / 2.2 packet \& time /
2.3 saturation modes / 2.4 1B vs 1K. Includes Figure~1.

%% ===================================================================
\section{Event-Level Time Reconstruction}\label{sec:method}
%% Task 8
TBD --- ~2.5 pages. Opens with framing as prerequisite for Section~\ref{sec:recovery}.
Subsections 3.1 problem / 3.2 SEC validation / 3.3 $\Delta s_{\rm time}=1$ direct LIS
(includes dead-zone safeguard sentence) / 3.4 $\Delta s_{\rm time}>1$ grouped LIS.
Includes Figures~2, 3, 4 and Table~1.

%% ===================================================================
\section{FIFO Reset Detection and Light Curve Recovery}\label{sec:recovery}
%% Task 10 --- HEADLINE SECTION
TBD --- ~2 pages. Opens with ``With per-event times reconstructed, we
address the headline problem''. Subsections 4.1 adaptive gap threshold /
4.2 unreliable interval flagging / 4.3 cross-box shape function /
4.4 three-box co-saturation degenerate case. Includes Figure~5.

%% ===================================================================
\section{Validation}\label{sec:validation}
%% Task 12
TBD --- ~3 pages. Subsections 5.1 internal 1B/1K consistency /
5.2 HE engineering data \textbf{(headline)} / 5.3 cross-satellite (5.3.1
time systems / 5.3.2 GBM / 5.3.3 SPI-ACS / 5.3.4 GECAM-C) /
5.4 cross-box cross-correlation. Includes Figures~6, 7, 8 and Tables~2, 3, 4.

%% ===================================================================
\section{Discussion: Limits and Failure Modes}\label{sec:discussion}
%% Task 14
TBD --- ~1.5 pages. Subsections 6.1 too bright / 6.2 too short /
6.3 silent drops (mechanism real but undetectable) / 6.4 CRC-failed event
recovery infeasibility. \textbf{Dead zone is NOT discussed here} ---
it appears only in \S\ref{sec:method} as a boundary safeguard.

%% ===================================================================
\section{Conclusion}\label{sec:conclusion}
%% Task 15
TBD --- ~0.5 pages. Four-bullet summary mirroring contribution list,
plus open-source pointer (Zenodo DOI to be inserted in Task 19).

%% ===================================================================
\section*{Code and Data Availability}
%% Task 19
TBD --- statement to be filled with Zenodo DOI after release tag.

\bibliographystyle{plain}
\bibliography{refs_en}

\end{document}
